\papertitle

### 2012-10-13 manuscript.tex
Trim abstract

%----------------------------------------------------------------------------%
% METADATA
\def \papertitle{Cooperative Control for Narrow Passage Traversal with an 
Ornithopter Micro Air Vehicle and Lightweight Ground Station}
\def \paperkeywords{AAMAS proceedings, multiagent systems, cooperative control, 
particle filter, micro air vehicle, ground station, visual servoing, pose 
estimation, flapping wing, ornithopter, biomimetic}
\def \paperterms{Algorithms, Performance, Design, Experimentation}
\def \paperauthors{Ryan C. Julian, Cameron J. Rose, Humphrey Hu, and Ronald S. Fearing}

@@

%% Paper number instead of authors
%\numberofauthors{1}
%\alignauthor Paper  580

\numberofauthors{4}
\author{
\alignauthor Ryan C. Julian\\
       \affaddr{Department of EECS}\\
       \affaddr{Univ. of California, Berkeley}\\
       \affaddr{Berkeley, CA 94720}\\
       \email{ryanjulian@berkeley.edu}
\alignauthor Cameron J. Rose\\
       \affaddr{Department of EECS}\\
       \affaddr{Univ. of California, Berkeley}\\
       \affaddr{Berkeley, CA 94720}\\
       \email{c\_rose@eecs.berkeley.edu}
\alignauthor Humphrey Hu\\
       \affaddr{Robotics Institute}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA 15213}\\
       \email{humhu@cmu.edu}
\and
\alignauthor Ronald S. Fearing\\
       \affaddr{Department of EECS}\\
       \affaddr{Univ. of California, Berkeley}\\
       \affaddr{Berkeley, CA 94720}\\
       \email{ronf@eecs.berkeley.edu}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
\begin{abstract}
The power, size, and weight constraints of micro air vehicles (MAVs) limit 
their on-board sensing and computational resources. Ground vehicles have 
less mobility than MAVs, but relaxed size constraints, and typically more 
computing power. These specializations present many opportunities for cooperation. In this work, we 
demonstrate cooperative target-seeking between a 13 gram ornithopter MAV 
and a lightweight ground station using computer vision. We demonstrate the performance of the location estimation and navigation algorithms. We develop models for the ornithopter, ground station, and cooperative system dynamics. We determine model parameters of the real systems through experimental system identification. Finally, we verify those models using experiments on narrow passage traversal, and arrive at a cooperative system model which accurately predicts the backwards-reachable region for successfully negotiating ornithopther flight through narrow openings.

We also introduce a new ornithopter MAV, the 13 gram H$^2$Bird. It 
features clap and fling wings, improves upon a previous design by 
utilizing a carbon fiber airframe, tail rotor, and elevator, and carries a 
payload of 2.8 grams. We augment the ornithopter's built-in 
gyroscope-based control with a lightweight ground station design, which has power and weight 
requirements appropriate for deployment on a millirobotic ground vehicle. The ground 
station provides heading estimates to the ornithoper by running a 
real-time motion tracking algorithm on a live video stream. This allows 
the ornithopter to reliably negotiate flight through narrow openings.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACM METADATA

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
The authors would like to thank Fernando Garcia Bermudez for his 
assistance with the Vicon motion capture system, Andrew Pullin for his 
help with robot photography, and the members of the Biomimetic 
Millisystems Laboratory and the EECS community at the University of 
California, Berkeley for their advice and support.

>>>>

%----------------------------------------------------------------------------%
% METADATA
\def \papertitle{Cooperative Control and Modeling for Narrow Passage Traversal with an 
Ornithopter MAV and Lightweight Ground Station}
\def \paperkeywords{AAMAS proceedings, multiagent systems, cooperative control, 
particle filter, micro air vehicle, ground station, visual servoing, pose 
estimation, flapping wing, ornithopter, biomimetic}
\def \paperterms{Algorithms, Performance, Design, Experimentation}
%\def \paperauthors{Ryan C. Julian, Cameron J. Rose, Humphrey Hu, and Ronald S. Fearing}
\def \paperauthors{Paper 580}

@@

%% Paper number instead of authors
\numberofauthors{1}
\author{
\alignauthor Paper  580
}

%\numberofauthors{4}
%\author{
%\alignauthor Ryan C. Julian\\
%       \affaddr{Department of EECS}\\
%       \affaddr{Univ. of California, Berkeley}\\
%       \affaddr{Berkeley, CA 94720}\\
%       \email{ryanjulian@berkeley.edu}
%\alignauthor Cameron J. Rose\\
%       \affaddr{Department of EECS}\\
%       \affaddr{Univ. of California, Berkeley}\\
%       \affaddr{Berkeley, CA 94720}\\
%       \email{c\_rose@eecs.berkeley.edu}
%\alignauthor Humphrey Hu\\
%       \affaddr{Robotics Institute}\\
%       \affaddr{Carnegie Mellon University}\\
%       \affaddr{Pittsburgh, PA 15213}\\
%       \email{humhu@cmu.edu}
%\and
%\alignauthor Ronald S. Fearing\\
%       \affaddr{Department of EECS}\\
%       \affaddr{Univ. of California, Berkeley}\\
%       \affaddr{Berkeley, CA 94720}\\
%       \email{ronf@eecs.berkeley.edu}
%}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
\begin{abstract}
The power, size, and weight constraints of micro air vehicles (MAVs) limit 
their on-board sensing and computational resources. Ground vehicles have 
less mobility than MAVs, but relaxed size constraints, and typically more 
computing power. These specializations present many opportunities for cooperation. 
In this work, we demonstrate cooperative target-seeking between a 13 gram 
ornithopter MAV and a lightweight ground station using computer vision. We 
develop models for the ornithopter, ground station, and cooperative system 
dynamics. We determine model parameters of the real systems through experimental 
system identification. Finally, we verify those models using experiments on 
narrow passage traversal, and arrive at a cooperative system model which 
accurately predicts the backwards-reachable region for successfully 
negotiating ornithopther flight through narrow openings.

We introduce a new ornithopter MAV, the 13 gram H$^2$Bird. It 
features clap and fling wings, improves upon previous designs by 
utilizing a carbon fiber airframe, tail rotor, and elevator, and carries a 
2.8 gram payload. We augment the ornithopter's built-in gyroscope-based 
control with a lightweight ground station design, which has power and weight 
requirements appropriate for deployment on a millirobotic ground vehicle. The ground 
station provides heading estimates to the ornithoper by running a real-time 
motion tracking algorithm on a live video stream.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACM METADATA

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Acknowledgments}
%The authors would like to thank Fernando Garcia Bermudez for his 
%assistance with the Vicon motion capture system, Andrew Pullin for his 
%help with robot photography, and the members of the Biomimetic 
%Millisystems Laboratory and the EECS community at the University of 
%California, Berkeley for their advice and support.
